
---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "README-")
```

#corpuslingr: 

Some r functions for (1) quick web scraping and (2) corpus seach of complex grammatical constructions in context. 

The two sets of functions can be used in conjunction, or independently.  In theory, one could build a corpus of the days news (as a dataframe in text interchange format), annotate the corpus using r-pacakges `cleanNLP`, `spacyr`, or `udap`, and subsequently search the corpus for complex grammtical constructions utilizing search functionality akin to that made available in the [BYU suite of corpora]().

The package facilitates regex/CQL-based search across form, lemma, and detailed part-of-speech tags. Multi-term search is also supported.  Summary functions allow users to aggregate search results by text & token frequency, view search results in context (kwic), and create word embeddings/co-occurrence vectors for each search term. 

The collection of functions presented here is ideal for usage-based linguists and digital humanists interested in fine-grained search of moderately-sized corpora.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(cleanNLP)
library(corpuslingr) #devtools::install_github("jaytimm/corpuslingr")
```


##Web scraping functions

The two web-based functions presented here more or less work in tandem.  

###clr_web_gnews()

The first, `clr_web_gnews`, simply pulls metadata based on user-specified search paramaters from the GoogleNews RSS feed.  

```{r}
dailyMeta <- corpuslingr::clr_web_gnews (search="New Mexico",n=30)

head(dailyMeta['titles'])
```


###clr_web_scrape()

The second function, `clr_web_scrape`, scrapes text from a vector of web addresses.  This can be supplied by the output from `clr_web_gnews`, or any dataframe with links to websites.  The function returns a [TIF](https://github.com/ropensci/tif#text-interchange-formats)-compliant dataframe, with each scraped text represented as a single row.  Metadata from output of `clr_web_gnews` is also included.

Both functions depend on functionality made available in the `boilerpipeR`, `XML`, and `RCurl` packages.

```{r}
nm_news <- dailyMeta %>% 
  corpuslingr::clr_web_scrape(link_var='links')
```


##Corpus preparation & annotation

###clr_prep_corpus

This function performs two tasks.  It elminates unnecessary whitespace from the text column of a corpus dataframe object.  Additionally, it attempts to trick annotators into treating hyphenated words as a single token.  With the exception of Stanford's CoreNLP (via `cleanNLP`), annotators tend to treat hyphenated words as multiple word tokens.  For linguists interested in word formation processes, eg, this is disappointing. There is likley a less hacky way to do this.

```{r}
nm_news <- nm_news %>% mutate(text = corpuslingr::clr_prep_corpus (text, hyphenate = TRUE))
```


###Annotate via cleanNLP and udpipe
For demo purposes, we use `udpipe` (via `cleanNLP`) to annotate the corpus dataframe object. The `cleanNLP` package is fantastic -- the author has aggregated three different annotators (spacy, CoreNLP, and `udpipe`) into one convenient pacakge.  There are pros/cons with each annotator; we won't get into these here.     

A benefit of `udpipe` is that it is dependency-free, making it super useful for classroom and demo purposes.
 
```{r message=FALSE, warning=FALSE}
cleanNLP::cnlp_init_udpipe(model_name="english",feature_flag = FALSE, parser = "none") 
ann_corpus <- cleanNLP::cnlp_annotate(nm_news$text, as_strings = TRUE) 
```


###clr_set_corpus()

This function gets the corpus ready for complex, tuple-based search.  Tuples are created, taking the form `<token,lemma,pos>`; tuple onsets/offsets are also set. Annotation output is homogenized, including column names, making things easier 'downstream.' Naming conventions established in the `spacyr` package are adopted here.    

Lastly, the function splits the corpus into a list of dataframes by document.  This is ultimately a search convenience.

```{r}
lingr_corpus <- ann_corpus$token %>%
  clr_set_corpus(doc_var='id', 
                  token_var='word', 
                  lemma_var='lemma', 
                  tag_var='pos', 
                  pos_var='upos',
                  sentence_var='sid',
                  NER_as_tag = FALSE)
```


###clr_desc_corpus() 

A simple function for describing corpus. As can be noted, not all of the user-specified (n=30) links were successfully scraped.  Not all websites care to be scraped.
```{r}
corpuslingr::clr_desc_corpus(lingr_corpus)$corpus
```

Text-based descritpives:
```{r}
head(corpuslingr::clr_desc_corpus(lingr_corpus)$text)
```



##Search & aggregation functions

After setting the tuples, text can now be rebuilt 
```{r}
paste(lingr_corpus[[5]]$tup[1:5], sep=" ",collapse=" ")
```


###An in-house corpus querying language (CQL)

A fairly crude corpus querying language
Should be 'copy and paste' at his point. See 'Corpus design' post. Tuples and complex corpus search.?

###clr_search_gramx()
```{r}
search1 <- "<_Vx> <up!>"

lingr_corpus %>%
  corpuslingr::clr_search_gramx(search=search1)%>%
  head ()
```

###clr_search_context()

This function allows ... output includes a list of data.frames.  `BOW` and `KWIC`

```{r}
search2 <- '<all!> <> <of!>'
found_egs <- corpuslingr::clr_search_context(search=search2,corp=lingr_corpus,LW=5, RW = 5)
```



```{r}
clr_nounphrase
```


###clr_get_freqs()
```{r}
lingr_corpus %>%
  corpuslingr::clr_search_gramx(search=search1)%>%
  corpuslingr::clr_get_freq(agg_var = 'lemma')%>%
  head()
```


###clr_context_kwic()
```{r}
search4 <- "<_Jx> <and!> <_Jx>"

corpuslingr::clr_search_context(search=search4,corp=lingr_corpus,LW=5, RW = 5)%>%
  corpuslingr::clr_context_kwic()%>%
  head()
```


###clr_context_bow()
Vector space model, or word embedding
```{r}
corpuslingr::clr_search_context(search=search4,corp=lingr_corpus,LW=5, RW = 5)%>%
  corpuslingr::clr_context_bow()%>%
  head()
```


###clr_search_keyphrases()

most of this is described more thoroughly in this [post](https://www.jtimm.net/blog/keyphrase-extraction-from-a-corpus-of-texts/).

The function leverages `clr_search_gramx()` .... uses tf-idf weights to extract keyphrases from each text comprising corpus.  The user can specify ... 

```{r}
clr_keyphrase
```



```{r}
lingr_corpus %>%
  corpuslingr::clr_search_keyphrases(n=5, key_var ='lemma', flatten=TRUE,jitter=TRUE)%>%
  head()
```

?Reference corpus.  
~Perhaps using SOTU.

##Multi-term search

```{r}
#multi-search <- c("")
search6 <- "<_xNP> (<wish&> |<hope&> |<believe&> )"
```


##Corpus workflow with corpuslingr, cleanNLP, & tidy

```{r eval=FALSE, message=FALSE, warning=FALSE}
corpuslingr::clr_web_gnews(search="New Mexico",n=30) %>%
  corpuslingr::clr_web_scrape(link_var='links') %>%
  cleanNLP::cnlp_annotate(as_strings = TRUE) %>%
  corpuslingr::clr_set_corpus(doc_var='id', 
                  token_var='word', 
                  lemma_var='lemma', 
                  tag_var='pos', 
                  pos_var='upos',
                  sentence_var='sid',
                  NER_as_tag = FALSE) %>%
  corpuslingr::clr_search_context(search=search2,LW=5, RW = 5)%>%
  corpuslingr::clr_context_kwic()
```



